### 2019-12-17 Draft_V5.tex
up

\begin{align}
\boldsymbol{F}=diag(c_{1}, c_{2}, \ldots c_{T-1})
\begin{bmatrix}
1 & \frac{-1}{T-1} & \cdots & \cdots & \frac{-1}{T-1}\\
\vdots & 1 & \frac{-1}{T-2} & \cdots & \frac{-1}{T-2}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \cdots & -1 
\end{bmatrix},
\end{align}    
where $c_{t}=\sqrt{\left( T-t\right)\left( T-t+1\right) }$.
Multiply $\boldsymbol{F}$ to model $(\ref{2})$, the model can expressed as  
\begin{align}
\tilde{\boldsymbol{y}}_{i}= \tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}+\tilde{\boldsymbol{u}}_{i},
\end{align}
where $\tilde{\boldsymbol{y}}_{i}=\boldsymbol{F}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}_{i,1}, \ldots, \tilde{\boldsymbol{y}}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}_{i}=\boldsymbol{F}\boldsymbol{W}_{i}= \left(\tilde{\boldsymbol{w}}_{i,1}, \ldots, \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}_{i}=\boldsymbol{F}\boldsymbol{u}_{i}= \left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}_{i,t}=c_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$ for $t=1, \ldots, T-1.$

@@

Then, we can define IV estimator in fixed effect model of $\boldsymbol{\theta}^{b}_{i}$ as
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{IV,i}= \left( \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{W}}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{y}}_{i},
\end{align}
where $\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}$ and $b=1$ corresponds to the fixed effects model while $b=2$ corresponds to the trend models.

The

@@

\section{Choosing the number of instruments}
When $\{ x_{i,t} \}^{T}_{t=1-j}$ for $j \geq 1$ are available $\left( j+1 \right)$ instruments can be used. And we also know that using more instruments, estimator are more efficient but more biased.

>>>>

\begin{align}
\boldsymbol{F}=diag(c_{1}, c_{2}, \ldots c_{T-1})
\begin{bmatrix}
1 & \frac{-1}{T-1} & \cdots & \cdots & \frac{-1}{T-1}\\
\vdots & 1 & \frac{-1}{T-2} & \cdots & \frac{-1}{T-2}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \cdots & -1 
\end{bmatrix},
\end{align}    
where $c_{t}=\sqrt{\left( T-t\right)\left( T-t+1\right) }$.
Multiply $\boldsymbol{F}$ to model $(\ref{2})$, the model can expressed as  
\begin{align}
\tilde{\boldsymbol{y}}_{i}= \tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}+\tilde{\boldsymbol{u}}_{i},
\end{align}
where $\tilde{\boldsymbol{y}}_{i}=\boldsymbol{F}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}_{i,1}, \ldots, \tilde{\boldsymbol{y}}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}_{i}=\boldsymbol{F}\boldsymbol{W}_{i}= \left(\tilde{\boldsymbol{w}}_{i,1}, \ldots, \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}_{i}=\boldsymbol{F}\boldsymbol{u}_{i}= \left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}_{i,t}=c_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$, for $t=1, \ldots, T-1.$

@@

Then, we can define IV estimator, $\boldsymbol{\theta}^{b}_{i}$, as
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{IV,i}= \left( \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{W}}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{y}}_{i},
\end{align}
where $\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}$ and $b=1$ corresponds to the fixed effects model while $b=2$ corresponds to the trend models.

If we can observe long lagged length from data, we have many instruments that can be used.
In empirical study, researchers do not use all past variables as instruments because there are trade off between efficiency and bias.
But we have not clearly know that the effect of using long lagged length  IV estimator in heterogeneous dynamic panel data model. And how to select the instruments to balance the bias and efficiency.

\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency. We try to follow this method to construct the optimal instruments. We define a weighting vector $\boldsymbol{W}=\left(w_{1}, \ldots, w_{j} \right)^{'}$. Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}\left(\boldsymbol{W} \right)= \sum^{J}_{j=1}w_{j} \boldsymbol{P}^{(j)}_{i},
\end{align}
where $J$ is maximum number of lagged variables that we can observed. 
Our goal is choosing $\boldsymbol{W}$ to minimize the approximate mean square error.

@@
